---
title: "wallace_addMods_IBS2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## *Wallace*

*Wallace* is a modular platform for reproducible modeling of species niches and distributions, written in R with the web app development package `shiny`. The application guides users through a complete analysis, from the acquisition of data to visualizing model predictions on an interactive map, thus bundling complex workflows into a single, streamlined interface.

*Wallace* is currently available via Github using `devtools::install_github('wallaceEcoMod/wallace')`. All development for the project occurs in this repository. You can get *Wallace* up and running with a few lines of code.

```{r, eval = FALSE}
# if you do not have devtools installed, install it first
install.packages("devtools", repos = "http://cran.us.r-project.org")
# install wallace from github
devtools::install_github("wallaceEcoMod/wallace")
# load wallace
library(wallace)
# run the user interface
wallace()
```

## *Wallace* is **Modular**

Developers can (and are encouraged to) contribute new methods to *Wallace* by submitting pull requests for new modules. This feature is key to the concept of *Wallace*, which was built for community expansion.

The way developers can do this may change in future versions, but we will provide a simple example of adding a module in the current framework.

## Architecture of *Wallace*

*Wallace* has 8 "components" that represent key steps of a niche/distributional modeling analysis. Within each component, there are a number of "modules", which represent methdological options for that particular step. For example, the sixth component **Model** has modules ***BIOCLIM*** and ***Maxent***.

For all `shiny` apps, there are two main parts: "ui" and "server". The UI part generates all the controls and displays of the user interface, while the server part runs all the functions in the background.

Within the `inst/shiny` folder, *Wallace* has a script for each part: `server.R` and `ui.R`. In addition, there are scripts that contain the modules for each component in `/modules`. These are `source()`ed in `server.R`. Adding a new module involves making edits to each of these scripts, as you'll need to add not only the functionality, but the buttons, checkboxes, maps, tables, etc. that the user interacts with and views.

## Let's add GAMs to *Wallace*

Say that for your particular research needs, you'd like to fit generalized additive models (GAMs) in addition to the models available in *Wallace*, and possibly compare the results.

You'll be working in `mods_comp6.R`, `server.R`, and `ui.R`. Let's start with the functionality for the UI.

### UI development

To start, you'll need to imagine what the user will need to input to *Wallace* in order to have your module work. In the case of GAMs (the simplest case), perhaps you envision users entering the variables that go into the model and specifying a smoothing parameter to apply to all variables.

```{r, eval = FALSE}

```




